Comparison of Learning Outcomes for Simulation-Based and Traditional Curricula for Statistical Inference in a Designed Educational Experiment

### 2015-06-04 DefenseSlides/DepartmentalSeminar/JobsTalk.Rnw
Last minute edits following runthrough with Heike

Study Goal: Compare student learning outcomes for under two introductory curricula for statistical inference in a designed educational experiment\\

@@

\begin{table}[hbtp]
\centering
\begin{tabular}{lrrr} \hline
 & Pillai's $\Lambda$ & Approx. F & Pr($>$$|$F$|$)\\ 
 \hline  
Midterm & \Sexpr{sprintf("%.4f",round(summarytab[1,2],4))} & \Sexpr{sprintf("%.4f",round(summarytab[1,3],4))} &
\Sexpr{sprintf("%.4f",round(summarytab[1,6],6))}\\ 
Lab 5 & \Sexpr{sprintf("%.4f",round(summarytab[2,2],4))} & \Sexpr{sprintf("%.4f",round(summarytab[2,3],4))} &
\Sexpr{sprintf("%.4f",round(summarytab[2,6],6))}\\ 
Treatment & \Sexpr{sprintf("%.4f",round(summarytab[3,2],4))} & \Sexpr{sprintf("%.4f",round(summarytab[3,3],4))} &
\Sexpr{sprintf("%.4f",round(summarytab[3,6],6))}\\ 
\hline
\end{tabular}
\end{table}

@@

\begin{frame}
    \frametitle{Simulation Study: Stage 1 Results}
\begin{table}[hbtp]
\centering
\begin{tabular}{ccccc} \hline
$\eta$ & $s_{\tau_1}$ & $\hat{\text{SE}}\left[\tau_1\right]$ & $s_{\tau_2}$ & $\hat{\text{SE}}\left[\tau_2\right]$\\ 
 \hline  
\Sexpr{sprintf("%.1f",round(simresults[1,1],1))} & \Sexpr{sprintf("%.4f",round(simresults[1,14],4))} & \Sexpr{sprintf("%.4f",round(simresults[1,16],4))} &\Sexpr{sprintf("%.4f",round(simresults[1,15],4))}  &\Sexpr{sprintf("%.4f",round(simresults[1,17],4))} \\
\Sexpr{sprintf("%.1f",round(simresults[2,1],1))} & \Sexpr{sprintf("%.4f",round(simresults[2,14],4))} & \Sexpr{sprintf("%.4f",round(simresults[2,16],4))} &\Sexpr{sprintf("%.4f",round(simresults[2,15],4))}  &\Sexpr{sprintf("%.4f",round(simresults[2,17],4))} \\
\Sexpr{sprintf("%.1f",round(simresults[3,1],1))} & \Sexpr{sprintf("%.4f",round(simresults[3,14],4))} & \Sexpr{sprintf("%.4f",round(simresults[3,16],4))} &\Sexpr{sprintf("%.4f",round(simresults[3,15],4))}  &\Sexpr{sprintf("%.4f",round(simresults[3,17],4))} \\
\Sexpr{sprintf("%.1f",round(simresults[4,1],1))} & \Sexpr{sprintf("%.4f",round(simresults[4,14],4))} & \Sexpr{sprintf("%.4f",round(simresults[4,16],4))} &\Sexpr{sprintf("%.4f",round(simresults[4,15],4))}  &\Sexpr{sprintf("%.4f",round(simresults[4,17],4))} \\
\Sexpr{sprintf("%.1f",round(simresults[5,1],1))} & \Sexpr{sprintf("%.4f",round(simresults[5,14],4))} & \Sexpr{sprintf("%.4f",round(simresults[5,16],4))} &\Sexpr{sprintf("%.4f",round(simresults[5,15],4))}  &\Sexpr{sprintf("%.4f",round(simresults[5,17],4))} \\
\Sexpr{sprintf("%.1f",round(simresults[6,1],1))} & \Sexpr{sprintf("%.4f",round(simresults[6,14],4))} & \Sexpr{sprintf("%.4f",round(simresults[6,16],4))} &\Sexpr{sprintf("%.4f",round(simresults[6,15],4))}  &\Sexpr{sprintf("%.4f",round(simresults[6,17],4))} \\
\hline
\end{tabular}
\end{table}

@@

Type I error rates increase as $c$ increases

@@

Steps taken to minimize non-treatment differences in classroom
    \begin{itemize}
        \item Alternation of instruction
        \item Identical curricula weeks 1 to 8
        \item Physical classrooms similar
    \end{itemize}

@@

>>>>

Study Goal: Compare student learning outcomes under two introductory curricula for statistical inference in a designed educational experiment\\

@@

\begin{table}[hbtp]
\centering
\begin{tabular}{lrrr} \hline
 & Pillai's $\Lambda$ & Approx. F & Pr($>$$|$F$|$)\\ 
 \hline  
Midterm & \Sexpr{sprintf("%.4f",round(summarytab[1,2],4))} & \Sexpr{sprintf("%.4f",round(summarytab[1,3],4))} &
0.0001\\ 
Lab 5 & \Sexpr{sprintf("%.4f",round(summarytab[2,2],4))} & \Sexpr{sprintf("%.4f",round(summarytab[2,3],4))} &
\Sexpr{sprintf("%.4f",round(summarytab[2,6],6))}\\ 
Treatment & \Sexpr{sprintf("%.4f",round(summarytab[3,2],4))} & \Sexpr{sprintf("%.4f",round(summarytab[3,3],4))} &
\Sexpr{sprintf("%.4f",round(summarytab[3,6],6))}\\ 
\hline
\end{tabular}
\end{table}

@@

@@

Type I error rates increase as $c$ decreases

@@

Steps taken to minimize non-treatment differences in classroom
    \begin{itemize}
        \item Alternation of instruction
        \item Identical curricula / shared class weeks 1 to 8
        \item Physical classrooms similar weeks 9 to 16
    \end{itemize}

@@

\begin{frame}
    \frametitle{Simulation Study: Additional Stage 1 Results}

\begin{table}[hbtp]
\centering
\begin{tabular}{ccccc} \hline
$\eta$ & $s_{\tau_1}$ & $\hat{\text{SE}}\left[\tau_1\right]$ & $s_{\tau_2}$ & $\hat{\text{SE}}\left[\tau_2\right]$\\ 
 \hline  
\Sexpr{sprintf("%.1f",round(simresults[1,1],1))} & \Sexpr{sprintf("%.4f",round(simresults[1,14],4))} & \Sexpr{sprintf("%.4f",round(simresults[1,16],4))} &\Sexpr{sprintf("%.4f",round(simresults[1,15],4))}  &\Sexpr{sprintf("%.4f",round(simresults[1,17],4))} \\
\Sexpr{sprintf("%.1f",round(simresults[2,1],1))} & \Sexpr{sprintf("%.4f",round(simresults[2,14],4))} & \Sexpr{sprintf("%.4f",round(simresults[2,16],4))} &\Sexpr{sprintf("%.4f",round(simresults[2,15],4))}  &\Sexpr{sprintf("%.4f",round(simresults[2,17],4))} \\
\Sexpr{sprintf("%.1f",round(simresults[3,1],1))} & \Sexpr{sprintf("%.4f",round(simresults[3,14],4))} & \Sexpr{sprintf("%.4f",round(simresults[3,16],4))} &\Sexpr{sprintf("%.4f",round(simresults[3,15],4))}  &\Sexpr{sprintf("%.4f",round(simresults[3,17],4))} \\
\Sexpr{sprintf("%.1f",round(simresults[4,1],1))} & \Sexpr{sprintf("%.4f",round(simresults[4,14],4))} & \Sexpr{sprintf("%.4f",round(simresults[4,16],4))} &\Sexpr{sprintf("%.4f",round(simresults[4,15],4))}  &\Sexpr{sprintf("%.4f",round(simresults[4,17],4))} \\
\Sexpr{sprintf("%.1f",round(simresults[5,1],1))} & \Sexpr{sprintf("%.4f",round(simresults[5,14],4))} & \Sexpr{sprintf("%.4f",round(simresults[5,16],4))} &\Sexpr{sprintf("%.4f",round(simresults[5,15],4))}  &\Sexpr{sprintf("%.4f",round(simresults[5,17],4))} \\
\Sexpr{sprintf("%.1f",round(simresults[6,1],1))} & \Sexpr{sprintf("%.4f",round(simresults[6,14],4))} & \Sexpr{sprintf("%.4f",round(simresults[6,16],4))} &\Sexpr{sprintf("%.4f",round(simresults[6,15],4))}  &\Sexpr{sprintf("%.4f",round(simresults[6,17],4))} \\
\hline
\end{tabular}
\end{table}

%---------------------------------------------------

\begin{frame}
    \frametitle{Simulation Study: Additional Stage 1 Results}

<<visual2, echo=FALSE , message=FALSE, warning=FALSE, fig.width=11, fig.height=3, out.width='.9\\linewidth', fig.pos='h',fig.align='center'>>=
srm <- melt(simresults, id.var="eta", measure.var=c("betamidterm1s", "betamidterm2s"))
levels(srm$variable) <- c("ConfMC","HypMC")

srm <- melt(errorsummary, id.var="eta", measure.var=c("T2ErrorRateBetaMidterm1", "T2ErrorRateBetaMidterm2"))
levels(srm$variable) <- c("ConfMC","HypMC")
ggplot(aes(x=eta, y=value, group=variable), data=srm) + 
  theme_bw() + 
  geom_point(size=4, aes(shape=variable)) + geom_line(aes(ltype=variable)) +
  ylab("Type II Error Rate") + xlab(expression(eta)) +
  scale_shape_discrete(name="Midterm Coefficients", labels=c(expression(paste("  ",beta[11])),expression(beta[12]))) +
  theme(legend.text = element_text(size = 12))
@

\center Type II error rates for midterm effect from 25,000 simulations at each $\eta$
